Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-29 MDPI_submission.Rmd
Commit 2023-11-29 14:14

```{r setup, echo=F, include=T, eval=TRUE}
## Load Clear Sky id v14.2 variables
MS <- data.frame(readRDS("~/CS_id/PARAMS/Clear_sky_id_Reno-Hansen_apply_v14_2.Rds"))
# export all Clear Sky variables
for (an in names(MS)) {
assign(an, MS[[an]])
}
## get TSI slope for reference
TSI <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
           strip.white = TRUE,
           sep = ";",
           header = TRUE))
TSI <- TSI[grep("TSI", TSI$var), ]
TSI$slope.sd           <- NULL
TSI$slope.ConfInt_0.95 <- NULL
TSI$slope.ConfInt_0.99 <- NULL
TSI$var                <- NULL
TSI$N                  <- NULL
TSI$Obs                <- NULL
setorder(TSI, -slope.stat_sig)
rownames(TSI) <- NULL
names(TSI) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
TSIslopeAll <- TSI[`Sky condition` == "All sky cond."]
```

>>>>

```{r setup, echo=F, include=T, eval=TRUE}
## Load Clear Sky id v14.2 variables
MS <- data.frame(readRDS("~/CS_id/PARAMS/Clear_sky_id_Reno-Hansen_apply_v14_2.Rds"))
# export all Clear Sky variables
for (an in names(MS)) {
assign(an, MS[[an]])
}
## get TSI slope for reference
TSI <- data.table(read.csv("./figures/tbl_longterm_trends.dat",
           strip.white = TRUE,
           sep = ";",
           header = TRUE))
TSI <- TSI[grep("TSI", TSI$var), ]
TSI$slope.sd           <- NULL
TSI$slope.ConfInt_0.95 <- NULL
TSI$slope.ConfInt_0.99 <- NULL
TSI$var                <- NULL
TSI$N                  <- NULL
TSI$Obs                <- NULL

TSI$cor.null_value     <- NULL
TSI$cor.alternative    <- NULL
TSI$cor.method         <- NULL
TSI$cor.data_name      <- NULL
TSI$cor.p              <- NULL
care <- grep("^cor\\.", names(TSI), value = T )
for (an in care) {
    TSI[, (an) := NULL ]
}

setorder(TSI, -slope.stat_sig)
rownames(TSI) <- NULL
names(TSI) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Trend statistical signif. [%]")
TSIslopeAll <- TSI[`Sky condition` == "All sky cond."]
```
